---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = TRUE,
  warning = TRUE,
  out.width = "100%",
  out.height = "500px",
  fig.pos = "center",
  dpi = 300
)
```

## ID and response

* 'id': unique identifier for the customer
* 'attrition_flag': whether the customer is churned (0 = no; 1 = yes)

##  Categorical

* 'gender': gender of the customer
* 'education_level': education level of the customer
* 'income_category': income range of the customer

# Numeric

* 'total_relationship_count': number of relationships
* 'months_inactive_12_mon': number of months the customer is inactive in the past 12 months
* 'credit_limit': the customer's credit limit
* 'total_revolving_bal': the customer's total revolving balance
* 'total_amt_chng_q4_q1': the amount the balance changed from Q4 to Q1
* 'total_trans_amt': the value of all the customer's transactions in the period
* 'total_trans_ct': the number of all of the customer's transactions
* 'total_ct_chng_q4_q1': the difference in number of the customer's transactions from Q4 to Q1
* 'avg_utilization_ratio': the customer's average utilization ratio during the period

Strategy:

* change attrition flag to "churned" yes/no
* create summarize_churn function early on
* for linear, log on credit limit (maybe others?)
* Lot of numeric, so xgboost early on
* Try turning income category and education level into ordinal numbers (unknown as either 0 or as mean impute)

EDA:

* Density of all numeric, comparing attrition and not
* AUC of attrition vs all predictors

* Relationship between relationships/months inactive (line plot)
* Credit limit, age, total revolving balance, total amt change, (density plot or bucketed line plot)
* gender, Education + income and churn (bar plot)
* Total relationships and churn (line plot)

```{r}

library(tidymodels)
library(tidyverse)
library(scales)
library(lubridate)
library(stacks)
theme_set(theme_light())

#doParallel::registerDoParallel(cores = 4)
```

```{r}
education_levels <- c("Unknown", "Uneducated", "High School", "College", "Graduate", "Doctorate", "Post-Graduate")
```

```{r}
process_data <- function(tbl) {
  tbl %>%
    mutate(education_level = fct_relevel(education_level, education_levels),
           income_category = fct_reorder(income_category, parse_number(income_category)),
           income_category = fct_relevel(income_category, "Less than $40K"))
}
```


```{r}
dataset <- read_csv("datasets/ep7/train.csv") %>%
  mutate(churned = factor(ifelse(attrition_flag == 1, "yes", "no"))) %>%
  select(-attrition_flag) %>%
  process_data()
holdout <- read_csv("datasets/ep7/test.csv") %>%
  process_data()

set.seed(2021)
spl <- initial_split(dataset)
train <- training(spl)
test <- testing(spl)

train_5fold <- train %>%
  vfold_cv(5)
```

```{r}
summarize_churn <- function(tbl) {
  tbl %>%
    summarize(n = n(),
              n_churned = sum(churned == "yes"),
              pct_churned = n_churned / n,
              low = qbeta(.025, n_churned + .5, n - n_churned + .5),
              high = qbeta(.975, n_churned + .5, n - n_churned + .5)) %>%
    arrange(desc(n))
}

plot_categorical <- function(tbl, category, ...) {
  if (!is.factor(pull(tbl, {{ category }}))) {
    tbl <- tbl %>%
      mutate({{ category }} := fct_reorder({{ category }}, pct_churned))
  }
  
  tbl %>%
    ggplot(aes(pct_churned, {{ category }}, ...)) +
    geom_col(position = position_dodge()) +
    geom_errorbarh(position = position_dodge(width = 1), aes(xmin = low, xmax = high), height = .2) +
    scale_x_continuous(labels = percent) +
    labs(x = "% in category that churned")
}

train %>%
  group_by(gender) %>%
  summarize_churn() %>%
  plot_categorical(gender)

train %>%
  group_by(education_level, gender) %>%
  summarize_churn() %>%
  plot_categorical(education_level, fill = gender, group = gender)

train %>%
  group_by(education_level) %>%
  summarize_churn() %>%
  plot_categorical(education_level) +
  coord_flip() +
  labs(x = "% churned",
       y = "Education",
       title = "How does churn risk differ by education")

train %>%
  group_by(income_category) %>%
  summarize_churn() %>%
  plot_categorical(income_category) +
  coord_flip() +
  labs(x = "% churned",
       y = "Income category",
       title = "How does churn risk differ by income category")

qplot(train$customer_age)
train %>%
  group_by(age = cut(customer_age, c(20, 40, 50, 60, 70))) %>%
  summarize_churn() %>%
  plot_categorical(age) +
  coord_flip()
```

Let's look at all numerics!

```{r}
gathered <- train %>%
  select(customer_age, total_relationship_count:churned) %>%
  gather(metric, value, -churned) %>%
  mutate(churned = str_to_title(churned))

gathered %>%
  ggplot(aes(value, fill = churned)) +
  geom_density(alpha = .5) +
  facet_wrap(~ metric, scales = "free") +
  scale_x_log10() +
  labs(title = "How do numeric metrics differ between churn/didn't churn?",
       subtitle = "All predictors on a log scale",
       x = "Log(predictor)",
       fill = "Churned?")

gathered %>%
  group_by(metric) %>%
  mutate(rank = percent_rank(value)) %>%
  ggplot(aes(rank, fill = churned)) +
  geom_density(alpha = .5) +
  facet_wrap(~ metric, scales = "free") +
  labs(title = "How do numeric metrics differ between churn/didn't churn?",
       subtitle = "All predictors on a percentile scale",
       x = "Percentile of predictor",
       fill = "Churned?")
```

Let's start building models!

XGBoost on ones that are clearly predictive or low cardinality.

```{r}
mset <- metric_set(mn_log_loss)
control <- control_grid(save_workflow = TRUE,
                        save_pred = TRUE,
                        extract = extract_model)
```

Trained a model on all the variables, with income and education turned into ordinal variables and "unknown" imputed to the mean (revisit that choice). 

```{r}
# Let's try 10-fold CV
set.seed(2021-07-13)
train_10fold <- train %>%
  vfold_cv(10)

factor_to_ordinal <- function(x) {
  ifelse(x == "Unknown", NA, as.integer(x))
}
```

```{r}
# Try all numeric, and turn categorical into ordinal
xg_rec <- recipe(churned ~ .,
                 data = train) %>%
  step_mutate(avg_transaction_amt = total_trans_amt / total_trans_ct) %>%
  step_mutate(income_category = factor_to_ordinal(income_category),
              education_level = factor_to_ordinal(education_level)) %>%
  step_impute_mean(all_numeric_predictors()) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_rm(id) %>%
  # For now, remove the formerly categorical ones (low importance)
  step_rm(income_category, education_level)



xg_wf <- workflow(xg_rec,
           boost_tree("classification",
                      trees = tune(),
                      mtry = tune(),
                      tree_depth = tune(),
                      learn_rate = tune()))

# Trying out tree depth
xg_tune <- xg_wf %>%
  tune_grid(train_10fold,
            metrics = mset,
            control = control,
            grid = crossing(trees = seq(400, 1600, 20),
                            mtry = c(2,3),
                            tree_depth = c(4,5),
                            learn_rate = c(.02)))

autoplot(xg_tune)

xg_tune %>%
  collect_metrics() %>%
  arrange(mean)
```

Next model: try removing total_trans_amt (now that we have avg_transaction_amt)

```{r}
xg_fit <- xg_wf %>%
  finalize_workflow(select_best(xg_tune)) %>%
  fit(train)

xg_fit %>%
  augment(test, type.predict = "prob") %>%
  mn_log_loss(churned, .pred_no)

importances <- xgboost::xgb.importance(model = extract_fit_engine(xg_fit))

importances %>%
  mutate(Feature = fct_reorder(Feature, Gain)) %>%
  ggplot(aes(Gain, Feature)) +
  geom_col()
```

Training our first xgboost model! A few selected predictors, mostly numeric.

CV log loss on:

* selected ~7 predictors is about .11
* Adding in rest of predictors, around .087
* Removing the (formerly) categorical ones, .0853
* Adding in average transaction amount: 0.085 (on holdout 0.0849)

Everything except education + income, added average transaction amount, mtry = 3, 780 trees, learn rate = .02

Attempt 2:

* Everything except education + income, added average transaction amount, mtry = 3, 1040 trees, learn rate = .02, tree depth = 5. On test set, .0835.

```{r}
xg_fit_full <- xg_wf %>%
  finalize_workflow(select_best(xg_tune)) %>%
  fit(dataset)

# Last check before out the door
xgboost::xgb.importance(model = extract_fit_engine(xg_fit_full))

xg_fit_full %>%
  augment(holdout) %>%
  select(id, attrition_flag = .pred_yes) %>%
  write_csv("~/Desktop/attempt2.csv")
```

Plan for second hour: more tuning on learn rate and max depth, and more EDA while that trains.

Soon, will do an variable importance plot on the full prediction.


## Riley's Session Below
```{r}
library(h2o)
h2o.init()
```

# Pre-process the data per DRob's recipe 
```{r}
baked_dataset_tbl <- xg_rec %>% prep() %>% bake(dataset) 
baked_dataset_tbl 
```

# Add data to h2o and verify
```{r}
library(gt)
train_h2_tbl <- as.h2o(baked_dataset_tbl)
h2o.describe(train_h2_tbl) %>% gt()
```

## Identify the response column

```{r}
y <- "churned"
y
```

## Identify the predictors

```{r}
x <- setdiff(names(train_h2_tbl), y)
x
```

```{r}
aml <- h2o.automl(
  y = y, 
  x = x,
  training_frame = train_h2_tbl,
  project_name = "sliced_ep7_refactored",
  max_runtime_secs = 300,
  seed = 07212021
)
```

## View Leaderboard
```{r}
leaderboard_tbl <- aml@leaderboard %>% as_tibble()
```

## Extract Model ID Names
```{r}
model_names <- leaderboard_tbl$model_id
```

## Extract Ensemble Model 
```{r}
ensemble_model <- h2o.getModel(model_names[1])
```

## Extract Metalearner Model within Ensemble Model
```{r}
metalearner_model <- h2o.getModel(ensemble_model@model$metalearner$name)
```

## Evaluate Variable (Model) Importance within the Metalearner Model
```{r}
h2o.varimp(metalearner_model) 

h2o.varimp_plot(metalearner_model)
```
## Evaluate Variable Importance in the Training Set (Select best Model)
```{r}
best_model <- h2o.getModel(leaderboard_tbl$model_id[2])
h2o.varimp_plot(best_model)
```
```{r}
library(broom)
best_model@parameters
```




